Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-26 EconGrowth.Rnw
Adjusting the formatting of the US figure.

<<setup, include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=4,
  fig.height=3.8,
  out.width=".45\\textwidth",
  out.height=".38\\textwidth",
  comment=NA)

@@

createCountryGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graph <- xyplot(iGDP ~ iYear, data=dataTable)
  return(graph)
}

#graph <- createCountryGraph("US")
print(createCountryGraph("US"))

>>>>

<<setup, include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=6,
  fig.height=4,
#  out.width=".45\\textwidth",
#  out.height=".38\\textwidth",
  comment=NA)

@@

createCountryInputGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
                  type="l",
                  scales=list(cex=1.5, tck=-1),
                  ylab="Indexed (1980=1)",
                  auto.key=list(columns=1))
  return(graph)
}

createCountryInputGraph("US")
